\documentclass[a4paper,12pt,draft,titlepage,openbib]{beamer}

\author{Pritvi Jheengut @zcoldplayer}
\title{An introduction to The seL4 Microkernel}
\subtitle{A secure and performant Microkernel}

\usepackage[size=a4, orientation=landscape, scale=3.5]{beamerposter}

\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

% Eliminate errors such as
% LaTeX Font Warning: Font shape `T1/cmss/m/n' in size <4> not available
% LaTeX Font Warning: Size substitutions with differences up to 1.0pt

\usepackage{hyperref}
\hypersetup{
  pdfcreator=pdflatex,
  pdffitwindow=true
}

\usepackage{verbatim}

\usepackage[french,UKenglish]{babel}
\usepackage{listings}

% \usepackage{pgf}
% \usepackage{xy}[all]
% \usepackage{graphicx}

% \usepackage{booktabs}

\mode<presentation>{

  \useoutertheme{infolines}
  \usecolortheme{whale}

  \definecolor{light}{HTML}{0088FF}
  \definecolor{confblue}{HTML}{111144}
  \definecolor{confred}{HTML}{771111}
  \definecolor{confyellow}{HTML}{FF5533}

  \setbeamercolor{alerted text}{bg=confblue!75,fg=confyellow!50}
  \setbeamercolor{block title}{bg=confblue!80,fg=white}
  \setbeamercolor{block body}{bg=confblue,fg=confyellow}
  \setbeamercolor{frametitle}{parent=confyellow,bg=confblue!90,fg=confred!70}
  \setbeamercolor{normal text}{fg=confyellow}
  \setbeamercolor{structure}{bg=confblue,fg=light!75}
  \setbeamercolor{Title bar}{fg=confred!90}
  \setbeamercolor{titlelike}{parent=confyellow,bg=confblue!90,fg=white!85}

  \setbeamercovered{transparent,dynamic}

  \setbeamertemplate{blocks}[rounded][shadow=true]
  \setbeamertemplate{background canvas}[vertical shading]
                    [top=confred,middle=confblue!95,bottom=light]

% \mode<handout>{\beamertemplatesolidbackgroundcolor{black!50}}

}

\subtitle{
}

% \date{ }

\begin{document}

\date[]{}

\maketitle

\section{CopyLeft License}

\frame{
  \frametitle{Copyleft License Attribution}

  Made with love using beamer, LaTeX and git.\\
  You can view at \href{https://github.com/Pritvi-DevConMU-MSCC/Introduction2seL4}
  {Introduction to seL4}

  \begin{alertblock}{This work is licensed under the LaTeX Project
      Public License.}
    To view a copy of this license, visit \\
    \url{https://www.latex-project.org/lppl.txt}
  \end{alertblock}

  \begin{alertblock}{This work is licensed under the Creative
      Commons Attribution 4.0 International License.}
    To view a copy of this license, visit \\
    \url{http://creativecommons.org/licenses/by/4.0/} or \\

    send a letter to \\
    Creative Commons, \\
    PO Box 1866, \\
    Mountain View, \\
    CA 94042, \\
    USA. \\
  \end{alertblock}
}

\section{Greetings}

\frame{
  \frametitle{Who Am I}

  \large

  \href{http://slackware.com/}{Geek@Slackware}

  \href{https://twitter.com/zcoldplayer}{twitter @zcoldplayer}

  \href{https://xmail.net/z.coldplayer}{zcoldplayer xmail Website}

  \href{http://metservice.intnet.mu/}{Work
    : SMTT@Meteorological.Services.mu}

  Active in many User group LUGM, MMC, MSCC, FECM, GDG\_MU \\
  and several other hackathons

  Passionate about how and why things work.

  Fervour Advocate of Free Libre and Open Source Software.

  \href{}{}

}

\frame{
  \frametitle{Who are you}

  \large

  \begin{block}{Would you mind tell me who you are?}
    \begin{enumerate}
    \item @twitter\_handle
    \item where you work
    \item email you want to share
    \item Hobbies
    \item purpose and expectations of this session
    \end{enumerate}
  \end{block}

}

\section{Community Groups in Mauritius}

\frame{
  \frametitle{Community Groups in Mauritius}

  \begin{block}{Healthy growth of Community Groups in Mauritius}
    This turn of the century has seen an uprising of Community groups in
    Mauritius in the field of the Digital World. The diversity has
    helped the exchange and sharing of innovative ideas, experience,
    bleeding edge technology, upcoming events, conferences in the
    Digital Island of the Republic of Mauritius.
  \end{block}

  \large

  This is a list of some of the active communities in Digital Mauritius.
  \begin{itemize}
  \item Linux User Group Meta, LUGM
  \item Mauritius Software Craftmanship Community, MSCC
  \item Mauritius Makers Community, MMC
  \item Front-End Coders Mauritius, FECM
  \item PHP User Group of Mauritius, phpMauritiusUG
  \item Symfonymu
  \item Google Developers Group Mauritius, GDG\_M
  \item Digital Marketing Mauritius
  \end{itemize}

}

\section{ }

\frame{
  \frametitle{ }

  \large

}
\section{ }

\frame{
  \frametitle{ }

  \large

}


\section{ }

\frame{
  \frametitle{ }

  \large

}
\section{ }

\frame{
  \frametitle{ }

  \large

}
\section{ }

\frame{
  \frametitle{ }

  \large

}
\section{ }

\frame{
  \frametitle{ }

  \large

}
\section{ }

\frame{
  \frametitle{ }

  \large

}
\section{ }

\frame{
  \frametitle{ }

  \large

}


\section{ }

\frame{
  \frametitle{ }

  \large

}
\section{ }

\frame{
  \frametitle{ }

  \large

}
\section{ }

\frame{
  \frametitle{ }

  \large

}
\section{ }

\frame{
  \frametitle{ }

  \large

}
\section{ }

\frame{
  \frametitle{ }

  \large

}

\section{ }

\frame{
  \frametitle{ }

  \large

}

\section{end}

\frame{
  \frametitle{Questions}

  \huge

  \begin{block}

    QUESTIONS!

  \end{block}

}

\end{document}



